---
title: "p8105_hw5_as6445"
author: "Ayako Sekiya"
date: "2022-11-05"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggridges)
library(patchwork)

library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2

```{r import}
homicide = 
  read_csv(file = "./data/homicide-data.csv")
```
There are `r nrow(homicide)` observations and `r ncol(homicide)` columns in the homicide data. The variables included are as following: `r colnames(homicide)`.  
Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the total number of homicides and the number of unsolved homicides (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r count and create}
homicide_data= homicide %>% 
  unite("city_state", city:state, remove = FALSE, sep=", ") %>% 
  group_by(city_state) %>% 
  count(disposition, name = "disp_count") %>% 
  pivot_wider(
    names_from= "disposition",
    values_from= "disp_count")%>% 
  janitor::clean_names() %>% 
  replace(is.na(.), 0) %>% 
  mutate(total=closed_by_arrest + open_no_arrest +closed_without_arrest,
        unsolved= closed_without_arrest +open_no_arrest)
```

For the city of Baltimore, MD, use the `prop.test` function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r baltimore}
prop.test(
  homicide_data %>%  filter(city_state == "Baltimore, MD") %>% pull(unsolved),
   homicide_data %>%  filter(city_state == "Baltimore, MD") %>% pull(total)) %>% 
  broom::tidy()
```

Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

```{r function}
homicide_prop = homicide_data %>% 
  mutate(
    proportions = map2(.x = unsolved, .y = total, ~prop.test(x = .x, n = .y)),
    tidied = map(.x = proportions, ~broom::tidy(.x))
  ) %>% 
  select(-proportions) %>% 
  unnest(tidied) %>% 
  select(city_state, estimate, conf.low,conf.high)
```

Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r plot}
homicide_plot= homicide_prop %>% 
  ggplot(aes(x = fct_reorder(city_state, estimate), y = estimate)) + 
  geom_point() +  
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

ggsave(path = "results", "homicide_plot.pdf")
```

## Problem 3

First set the following design elements:

Fix n=30
Fix σ=5

Set μ=0. 

#### Create Simulation
```{r simulate}
simulations = function(mu=0, n=30, sigma = 5) {
  
  sim_data = tibble(
    x = rnorm(n , mean=mu, sd = sigma),
  )
  
    t.test(sim_data) %>%
    broom::tidy() %>%
    select(estimate,p.value)
}
```

Generate 5000 datasets from the model:

```{r}
expand_grid(
  means = 0,
  iteration = 1:5000
) %>%
  mutate(
    estimate_df = map(means, simulations)
  ) %>%
  unnest(estimate_df)
```

Simulate for μ={1,2,3,4,5,6}:

```{r}
sim_results_df = 
  expand_grid(
    means = c(1, 2, 3, 4, 5, 6),
    iteration = 1:5000
  ) %>% 
  mutate(
    estimate_df = map(means, simulations)
  ) %>%
  unnest(estimate_df)
```

#### Create first plot

Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.

```{r power}
plot1 = 
  sim_results_df %>%
  group_by(means) %>%
  summarize(
    rejected = sum(p.value < 0.05, na.rm = TRUE)/5000
  ) %>%
  ggplot(aes(x = means, y = rejected)) + 
    geom_point(alpha = .5, size = 3) + 
    geom_line()
  labs(
    title = "Power of t-test for true mean value",
    x = "True mean",
    y = "Power"
  )

plot1

ggsave("results/plot1.pdf", plot1, width = 20, height = 10)
```

When the true value of mu increases, power also increases.

#### Create some more plots!

Make a plot showing the average estimate of μ on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. 

```{r estimates}
estimateplot=
  sim_results_df %>%
  group_by(means)%>%
    summarize(estimate_mean=mean(estimate))
```

```{r overlay}
overlay = 
  sim_results_df %>%
  filter(p.value < 0.05) %>%
  group_by(means) %>%
  summarize(
    estimate_mean = mean(estimate)
  ) %>%
  ggplot(aes(x = means, y = estimate_mean, color = "rejected samples")) + 
  geom_point() +
  geom_line() +
  geom_point(data = estimateplot, aes(color = "all samples")) +
  geom_line(data = estimateplot, aes(color = "all samples")) +
  scale_color_manual(
    name = "Legend",
    breaks = c("rejected samples", "all samples"),
    values = c("rejected samples" = "red", "all samples" = "blue")) +
  labs(
    title = "Mean estimate for true means comparing samples when rejected null and for all samples",
    x = "True mean",
    y = "Mean estimate",
  )

overlay

ggsave("results/overlayplot.pdf", overlay, width = 20, height = 10)
```

Based on the plot, when the true mu is 0, the estimate mu of rejecting the null are greater than the true value of mu.
When the true value of mu increases, the averages of mu when the null is rejected gets closer to the true mu until the true value of mu is 4. After this point, the averages of mu rejecting the null and the true value of mu are very close together. 

